An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-06 poly-embed-journal/poly-embed-journal.tex
meeting edits?

To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
For condition (i), it is straightforward to check that $\hinge(\varphi(r))_y = \hinge(r)_y = 2 \Ind{r \neq y} = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
% First, consider that
% \begin{align*}
% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
% \end{align*}
% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p\in\simplex$:
\[
\prop{\ellzo}(p) = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\qquad
\prop{L_{hinge}}(p) = \begin{cases}
[1,\infty) & p_1 = 1\\
1 & p_1 \in (1/2,1) \\
[-1,1] & p_1 = 1/2\\
-1& p_1 \in (0, 1/2)\\
(-\infty, -1]& p_1 = 0
\end{cases}~.
\]
% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$.
By results in \S~\ref{subsec:match-BR}, one could also show that $\hinge$ embeds $2\ellzo$ by the fact that their Bayes risks match (Figure~\ref{fig:bayes-risks-01}).\jessiet{I like this foreshadowing, but think we should move the figure down to \S 6.}

\begin{figure}
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{figs/0-1-br.pdf}
%		\caption{Bayes risk of the 0-1 loss.}
%		\label{fig:0-1-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering		\includegraphics[width=0.95\linewidth]{figs/hinge-br.pdf}
%		\caption{Bayes risk of hinge loss.}
%		\label{fig:hinge-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{figs/logistic-br.pdf}
%	\caption{Bayes risk of the logistic loss.}
%	\label{fig:logistic-br}
\end{minipage}
\caption{Bayes risks $\risk L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = \Pr[Y=1]$.
	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise linear and concave, while the Bayes risk of logistic loss is not piecewise linear.  Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks, confirming that hinge loss (M) embeds 0-1 loss (L), but logistic loss (R) does not. \raf{Take a step back and ask: what point do we (want to) make with this figure? Seems a shame not to mention the Bayes risk matching of the first two and how that relates to embedding.}\jessie{Big picture: there's something eerily similar about Bayes risks when embedding is in the picture.  In fact, Bayes risks match.  This was originally up here when the BR matchinf result was way earlier.  I think it provides some nice intuition if you understand what's going on, but it might be more helpful closer to that result.  Otherwise, we're just introducing more things}}
\label{fig:bayes-risks-01}
\end{figure}

%% embedding yields calibration
In this particular example, it is known $(\hinge,\sgn)$ is calibrated with respect to 0-1 loss.
More generally, however, it is not clear whether an arbitrary embedding yields a calibrated link.
Indeed, apart from mapping the embedded points back to their original reports, via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
When the surrogate is polyhedral, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings always yield calibration.
\jessiet{Commented out next setence since it didn't really vibe with rest of paragraph to me - Mar 24 22}
%We first explore in \S~\ref{sec:poly-loss-embed} the connection between embeddings and polyhedral surrogates.

%% note that embedding is sufficient, but not necessary
\jessiet{Does this location for this point make sense?}
While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.

@@

A first observation is that if a loss $L$ elicits a property $\Gamma$, then $L$ restricted to some representative set $\Sc$, denoted $L|_\Sc$, elicits $\Gamma$ restricted to $\Sc$. \jessiet{Already in the notation... delete this?}
As a consequence, restricting to representative sets preserves the Bayes risk.
We will use these observations throughout.
\begin{lemma}\label{lem:loss-restrict}
  Let $L:\R\to\reals^\Y_+$ elicit $\Gamma$, and let $\Sc\subseteq\R$ be representative for $L$.
  % such that $\Gamma(p) \cap \Sc \neq \emptyset$ for all $p\in\simplex$.
  Then $L|_\Sc$ elicits $\gamma:\simplex\toto\Sc$ defined by $\gamma(p) = \Gamma(p)\cap \Sc$.
  Moreover, $\risk{L}=\risk{L|_\Sc}$.
\end{lemma}
\begin{proof}
  Let $p\in\simplex$ be fixed throughout.
  First let $r \in \gamma(p) = \Gamma(p) \cap \Sc$.
  Then $r \in \Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$, so as $r\in\Sc$ we have in particular $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  For the other direction, suppose $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  As $\Sc$ is representative for $L$, we must have some $s \in \Gamma(p) \cap \Sc$.
  On the one hand, $s\in\Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$.
  On the other, as $s \in \Sc$, we certainly have $s \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(s)}$, and thus $r \in \argmin_{u\in\R} \inprod{p}{L(u)} = \Gamma(p)$ as well.
  We now see $r \in \Gamma(p) \cap \Sc$.
  Finally, the equality of the Bayes risks $\min_{u\in\R} \inprod{p}{L(u)} = \min_{u\in\Sc} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\Sc \subseteq \Gamma(p)$ for all $p\in\simplex$.
\end{proof}

@@

With Proposition~\ref{prop:representative-embeds-restriction} in hand, we now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
While polyhedral surrogates cannot elicit finite properties, in the sense that they have infinitely many possible reports, they do elicit properties with a finite range, meaning they have finite representative sets.
%This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
See \S~\ref{app:power-diagrams} for the full proof of Lemma~\ref{lem:polyhedral-range-gamma}.

@@

\jessiet{Do we want this paragraph?- May 3, 22}
While Theorem~\ref{thm:discrete-loss-poly-embeddable} constructs a consistent surrogate for any discrete loss, in some settings, such as structured prediction and information retrieval, the prediction dimension $d = n := |\Y|$ (e.g., $d$ such that $L : \reals^d \to \reals^\Y_+$) can be prohibitively large.%
\footnote{One can always reduce to $d=n-1$ in Theorem~\ref{thm:discrete-loss-poly-embeddable} via a linear transformation from $\reals^n$ to $\reals^{n-1}$ which is injective on $\simplex$; redefining the surrogate appropriately, the Bayes risks will still match.}
Recent work~\citep{ramaswamy2016convex,finocchiaro2020embedding,finocchiaro2021unifying} yield characterizations for bounding the prediction dimension $d$ for consistent convex surrogates and embeddings.
%\raft{I trimmed this discussion and footnoted the $n-1$ construction, and then folded the last paragraph above the theorem \jessie{I like this much better}}

\section{Consistency via Calibrated Links}
\label{sec:calibration}

We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$).
But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate. \jessiet{Haven't defined calibrated yet, so maybe want to say consistent? idk what is best - May 3, 22}
\jessie{in link state: calibrated vs consistent?}

@@

For \emph{(b)}, we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
For any $p \in \simplex$, consider the optimal surrogate report set, i.e. set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$. \jessiet{Adding ``for any $p$'' quantification - May 3, 22 \# burn}
By indirect elicitation, $\psi$ is already correct on $U$.
Now, we ``thicken'' $U$ to obtain $U_{\epsilon} = \{u : \|u - U\| \leq \epsilon\}$.
Then we require that all points in $U_{\epsilon}$ are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
For $\epsilon > 0$, this directly implies separation.

@@

Given the above proof sketch, the following construction is relatively straightforward.
We initialize the link using the embedding points and optimal report sets, then use $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points.
\begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, define $\U = \{\Gamma(p) : p \in \simplex\}$.
  For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
  First, initialize the \emph{link envelope} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{construction}

@@

Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
\jessie{Ref top k section?}

\bo{Should we comment on computing the $\epsilon$?}
\raf{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}

@@

%% overview of the applications
Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as to verify consistency or inconsistency for specific surrogate and link pairs.
Below, we illustrate the power of this framework with specific examples from the literature.
To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, which is an embedding, and show how to rederive their link function and surrogate regret bounds (\S~\ref{sec:abstain}). 
We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), multiclass classification (\S~\ref{sec:winge}), and top-$k$ classification (\S~\ref{sec:top-k}).
In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets for which they are consistent.
In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which would likely have been extremely challenging to derive without our framework. \jessiet{Want to be careful on this claim and make sure it doesn't sound like we do both surrogate and link for both.}

%% how to apply the embedding framework
% When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds $\ell_{\mathrm{embed}}$, in order to compare $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
% To this end, we suggest the following general approach.
% First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
% %Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
% Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
% By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
% From here one can further remove redundant reports until one arrives at a tight embedding if desired.
% Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it calibrated for the original problem (\S~\ref{sec:top-k}, \ref{sec:winge}).
% Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
% A key step in Construction~\ref{const:eps-thick-link} is constructing the set-valued link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}) or construct new calibrated links(\S~\ref{sec:lovasz-hinge}).
When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To this end, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
Second, identify the vertices of these polyhedral regions.%
\footnote{In some cases, these regions do not have vertices, such as the top-$k$ surrogates which are invariant in the all-ones direction; here one can restrict to a subspace, or otherwise select among equivalent reports.}
Third, conclude that the union of these vertices, $\Sc\subset\reals^d$, is a finite representative set for $L$.
% ~\citep[Statement 3.1.7]{grunbaum2013convex}.
Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
From here one can further remove redundant reports until one arrives at a tight embedding if desired.
Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it consistent for the original problem.

%% also interesting to use Sec 4 to verify proposed canonical links
With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. \jessiet{Redundant from \S 4 but I think that's okay.  I like it in both spots}
Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.

@@

%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular, and thus $\ell^f$ is a weighted Hamming loss.
Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.\jessiet{Changing $S$ to $A$ to not override notation from the submodular function.}
The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem is a special case of the Lov\'asz hinge.

@@

>>>>

To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
For condition (i), it is straightforward to check that $\hinge(\varphi(r))_y = \hinge(r)_y = 2 \Ind{r \neq y} = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
% First, consider that
% \begin{align*}
% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
% \end{align*}
% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p\in\simplex$:
\[
\prop{\ellzo}(p) = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\qquad
\prop{L_{hinge}}(p) = \begin{cases}
[1,\infty) & p_1 = 1\\
1 & p_1 \in (1/2,1) \\
[-1,1] & p_1 = 1/2\\
-1& p_1 \in (0, 1/2)\\
(-\infty, -1]& p_1 = 0
\end{cases}~.
\]
% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
With both conditions of Definition~\ref{def:loss-embed} satisfied, we can conclude that $\hinge$ embeds $2\ellzo$.
By results in \S~\ref{subsec:match-BR}, one could also show that $\hinge$ embeds $2\ellzo$ by the fact that their Bayes risks match (Figure~\ref{fig:bayes-risks-01}).

\begin{figure}
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{figs/0-1-br.pdf}
%		\caption{Bayes risk of the 0-1 loss.}
%		\label{fig:0-1-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering		\includegraphics[width=0.95\linewidth]{figs/hinge-br.pdf}
%		\caption{Bayes risk of hinge loss.}
%		\label{fig:hinge-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.95\linewidth]{figs/logistic-br.pdf}
%	\caption{Bayes risk of the logistic loss.}
%	\label{fig:logistic-br}
\end{minipage}
\caption{Bayes risks $\risk L : p \mapsto \inf_u \inprod{p}{L(u)}$ of 0-1, hinge, and logistic losses, respectively, plotted as a function of $p_1 = \Pr[Y=1]$.
	Observe that the Bayes risks of 0-1 and hinge loss are both piecewise linear and concave, while the Bayes risk of logistic loss is not piecewise linear.  Proposition~\ref{prop:embed-bayes-risks} states that embedding is equivalent to matching Bayes risks, confirming that hinge loss (M) embeds 0-1 loss (L), but logistic loss (R) does not.}
\label{fig:bayes-risks-01}
\end{figure}

%% embedding yields calibration
In this particular example, it is known $(\hinge,\sgn)$ is calibrated with respect to 0-1 loss.
More generally, however, it is not clear whether an arbitrary embedding yields a calibrated link.
Indeed, apart from mapping the embedded points back to their original reports, via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
Using the strong connection between embeddings and polyhedral surrogates in \S~\ref{sec:poly-loss-embed}, we give a construction to map the remaining values in \S~\ref{sec:calibration}, showing that embeddings from polyhedral surrogates always yield calibration.

While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that it is not \emph{necessary} for these conditions.  
For example, while logistic loss does not embed 0-1 loss, the surrogate and link for logistic loss are consistent.

@@

A first observation is that if a loss $L$ elicits a property $\Gamma$, then $L$ restricted to some representative set $\Sc$, denoted $L|_\Sc$, elicits $\Gamma$ restricted to $\Sc$.
As a consequence, restricting to representative sets preserves the Bayes risk.
We will use these observations throughout.
\begin{lemma}\label{lem:loss-restrict}
  Let $L:\R\to\reals^\Y_+$ elicit $\Gamma$, and let $\Sc\subseteq\R$ be representative for $L$.
  % such that $\Gamma(p) \cap \Sc \neq \emptyset$ for all $p\in\simplex$.
  Then $L|_\Sc$ elicits $\gamma:\simplex\toto\Sc$ defined by $\gamma(p) = \Gamma(p)\cap \Sc$.
  Moreover, $\risk{L}=\risk{L|_\Sc}$.
\end{lemma}
\begin{proof}
  Let $p\in\simplex$ be fixed throughout.
  First let $r \in \gamma(p) = \Gamma(p) \cap \Sc$.
  Then $r \in \Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$, so as $r\in\Sc$ we have in particular $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  For the other direction, suppose $r \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  As $\Sc$ is representative for $L$, we must have some $s \in \Gamma(p) \cap \Sc$.
  On the one hand, $s\in\Gamma(p) = \argmin_{u\in\R} \inprod{p}{L(u)}$.
  On the other, as $s \in \Sc$, we certainly have $s \in \argmin_{u\in\Sc} \inprod{p}{L(u)}$.
  But now we must have $\inprod{p}{L(r)} = \inprod{p}{L(s)}$, and thus $r \in \argmin_{u\in\R} \inprod{p}{L(u)} = \Gamma(p)$ as well.
  We now see $r \in \Gamma(p) \cap \Sc$.
  Finally, the equality of the Bayes risks $\min_{u\in\R} \inprod{p}{L(u)} = \min_{u\in\Sc} \inprod{p}{L(u)}$ follows immediately by the above, as $\emptyset \neq \Gamma(p)\cap\Sc \subseteq \Gamma(p)$ for all $p\in\simplex$.
\end{proof}

@@

\raft{Need to combine/unify the filler text here and next paragraph}
With Proposition~\ref{prop:representative-embeds-restriction} in hand, we now shift our focus to \emph{polyhedral} (piecewise-linear and convex) surrogates.
While polyhedral surrogates cannot elicit finite properties, in the sense that they have infinitely many possible reports, they do elicit properties with a finite range, meaning they have finite representative sets.
%This observation lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
See \S~\ref{app:power-diagrams} for the full proof of Lemma~\ref{lem:polyhedral-range-gamma}.

@@

\section{Consistency via Separated Links \raf{revisit title?}}
\label{sec:calibration}

We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
The embedding itself tells us how to link the embedded points back to the discrete reports (map $\varphi(r)$ to $r$).
But it is not clear how to extend this to yield a full link function $\psi: \reals^d \to \R$, and whether such a $\psi$ can lead to consistency.
In this section, we prove Theorem~\ref{thm:link-main}, restated below, which gives a construction to generate calibrated links for \emph{any} polyhedral surrogate.

@@

For \emph{(b)}, we show that this link can be ``thickened'' by some positive $\epsilon$, as described next.
For any $p \in \simplex$, consider the optimal surrogate report set, i.e.\ set of the form $U = \Gamma(p) = \argmin_u \inprod{p}{L(u)}$.
By indirect elicitation, $\psi$ is already correct on $U$.
Now, we ``thicken'' $U$ to obtain $U_{\epsilon} = \{u : \|u - U\| \leq \epsilon\}$.
Then we require that all points in $U_{\epsilon}$ are linked to some element of $\gamma(p) = \argmin_r \inprod{p}{\ell(r)}$.
For $\epsilon > 0$, this directly implies separation.

@@

Given the above proof sketch, the following construction is relatively straightforward.
We initialize the link using the embedding points and optimal report sets, then use $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points.
\begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, define $\U = \{\Gamma(p) : p \in \simplex\}$.
  % For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
  First, initialize the \emph{link envelope} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \R : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{construction}

@@

Applying the $\epsilon$-thickened link construction additionally enables one to verify the consistency of a proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
See \S~\ref{sec:top-k} for an illustration of this test.

\botodo{Should we comment on computing the $\epsilon$?}
\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}

@@

%% overview of the applications
Our results give a framework to construct consistent polyhedral surrogates and link functions for any discrete target loss, as well as to verify consistency or inconsistency for specific surrogate and link pairs.
Below, we illustrate the power of this framework with specific examples from the literature.
To warm up, we study the abstain surrogate given by~\citet{ramaswamy2018consistent}, which is an embedding, and show how to rederive their link function and surrogate regret bounds (\S~\ref{sec:abstain}). 
We then give three examples of subsequent works that use our framework, in the context of structured binary classification (\S~\ref{sec:lovasz-hinge}), multiclass classification (\S~\ref{sec:winge}), and top-$k$ classification (\S~\ref{sec:top-k}).
In all cases, our framework illuminates the behavior of inconsistent surrogates by revealing the discrete losses they embed, i.e., the true targets for which they are consistent.
In structured binary classification and top-$k$ classification, our framework also gives new consistent surrogates and link functions which appear challenging to derive otherwise.

%% how to apply the embedding framework
% When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds $\ell_{\mathrm{embed}}$, in order to compare $\prop{\ell_{\mathrm{embed}}}$ to the property elicited by the proposed target $\prop{\ell}$.
% To this end, we suggest the following general approach.
% First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
% %Often these regions are straightforward to identify based on the form of $L$.\jessie{tbh prev sentence feels like a lie lol}
% Letting $\Sc\subset\reals^d$ be the union of vertices of these polyhedral regions, conclude that $\Sc$ is a finite representative set for $L$~\citep[Statement 3.1.7]{grunbaum2013convex}.
% By Proposition~\ref{prop:representative-embeds-restriction}, $L$ embeds $L|_\Sc$.
% From here one can further remove redundant reports until one arrives at a tight embedding if desired.
% Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it calibrated for the original problem (\S~\ref{sec:top-k}, \ref{sec:winge}).
% Moreover, while embedding guarantees the existence of a calibrated link function, Construction~\ref{const:eps-thick-link} provides a framework to both verify proposed link functions and construct new ones.
% A key step in Construction~\ref{const:eps-thick-link} is constructing the set-valued link candidate function $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to; this in turn provides a tool to verify the calibration of a proposed link (\S~\ref{sec:abstain}, \ref{sec:top-k}) or construct new calibrated links(\S~\ref{sec:lovasz-hinge}).

\subsection{Applying the embedding framework}
When using our framework to study the (in)consistency of an existing surrogate $L:\reals^d \to \reals^\Y_+$, often the first step is determining the loss it embeds.
To this end, we suggest the following general approach.
First, for each $y\in\Y$, divide $\reals^d$ into a finite number of polyhedral regions on which $L(\cdot)_y$ is an affine function.
Second, identify the vertices of these polyhedral regions.%
\footnote{In some cases, these regions do not have vertices, such as the top-$k$ surrogates which are invariant in the all-ones direction; here one can restrict to a subspace, or otherwise select among equivalent reports.}
Third, conclude that the union of these vertices, $\Sc\subset\reals^d$, is a finite representative set for $L$.
% ~\citep[Statement 3.1.7]{grunbaum2013convex}.
Now $L$ embeds $L|_\Sc$ from Proposition~\ref{prop:representative-embeds-restriction}.
From here one can further remove redundant reports until one arrives at a tight embedding if desired.
Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it consistent for the original problem.

\raf{Follow-up paragraph on prev sentence using abstain as an example}

%% also interesting to use Sec 4 to verify proposed canonical links
\raft{Rework so emphasis is more on the general construction and less on testing a given link}
With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. \jessiet{Redundant from \S 4 but I think that's okay.  I like it in both spots}
Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.

@@

%% lovasz paper closes the gap, answering inconsistency wrt \ell^f by showing that L^f embeds structured abstain
\citet{ourlovaszpaper} use our embedding framework to resolve the consistency of $L^f$, showing that it is inconsistent with respect to $\ell^f$ outside of the trivial case where $f$ is modular, and thus $\ell^f$ is a weighted Hamming loss.
Moreover, they show that $L^f$ embeds a variant $\ellabs$ of $\ell^f$ where one is allowed to abstain on a set of indices $A \subseteq [k]$, which they call the \emph{structured abstain problem}.
The inclusion of abstain options is natural when observing that the BEP surrogate $L^{1/2}$ from \S~\ref{sec:abstain} coincides with $L^f$ for the function $f(S) = \ones\{S \neq \emptyset\}$, so the multiclass abstain problem is a special case of the Lov\'asz hinge.

@@

\item Prediction dimension in general:
